Cryptanalysis of SBC based post-quantum signature scheme \\\textit{Graduation internship report}

### 2025-07-23 rapport.tex
page de garde

\author{Paul Mekhail
	\thanks{\texttt{paul.mekhail4@pm.me}}}
\affil{Laboratoire MIS, Université de Picardie Jules Verne, Amiens, France\\Sorbonne Université, Paris, France}

\author{\textbf{Advisor}: Sorina Ionica
	\thanks{\texttt{sorina.ionica@u-picardie.fr}}}
\affil{Laboratoire MIS, Université de Picardie Jules Verne, Amiens, France}

\title{Cryptanalysis of SBC based post-quantum signature scheme \\\textit{Graduation internship report}}

\begin{document}
	\maketitle

@@

		\begin{figure}[H]
			\begin{center}
				\includegraphics[scale=0.04]{unilasalle.jpg}
				\caption{UniLaSalle Engineering School, where the MIS offices are located(for now). Observant readers may notice the unusual UFO-like structure situated in front of the building.}
			\end{center}	
		\end{figure}

	\newpage
	\tableofcontents
	\newpage
	\section{MPC-in-the-Head and SBC signature scheme}\label{sec2}

>>>>

\newcommand{\maketitlepage}{
	\begin{titlepage}
		\centering
		% Logos
		\includegraphics[width=0.3\textwidth]{LOGO_SU_HORIZ_SEUL_CMJN.png} \hfill
		\includegraphics[width=0.2\textwidth]{Logo-UPJV-bleu.png} \\[1cm]

		% Noms des établissements
		{\large \textbf{Sorbonne Université}} \\ 
		{\large \textbf{Université de Picardie Jules Verne}} \\[0.5cm]

		% Nom du Master
		{\Large Master of Computer Science} \\
		{\large Cryptology, High-performance Computing, and Algorithms} \\[1.5cm]

		% Titre entouré de lignes
		\noindent\rule{\textwidth}{1pt} \\[0.4cm]
		{\Huge \textbf{Cryptanalysis of SBC-based Post-Quantum Signature Scheme}} \\[0.4cm]
		\noindent\rule{\textwidth}{1pt} \\[1.5cm]

		% Sous-titre
		{\Large Graduation Internship Report} \\
		{\large 2025} \\[2cm]

		% En bas de page, deux colonnes : auteur à gauche, encadrants à droite
		\vfill
		\begin{minipage}[t]{0.45\textwidth}
			\raggedright
			\textbf{Author:} \\
			Paul Mekhail \\
			Sorbonne Université, Université de Picardie Jules Verne \\
			\texttt{paul.mekhail4@pm.me}
		\end{minipage}
		\hfill
		\begin{minipage}[t]{0.45\textwidth}
			\raggedleft
			\textbf{Supervisor:} \\
			Sorina Ionica \\
			Laboratoire MIS, Université de Picardie Jules Verne \\
			\texttt{sorina.ionica@u-picardie.fr} \\[0.5cm]
			\textbf{Academic Supervisor:} \\
			Mohab Safey El Din \\
			LIP6, Sorbonne Université \\
			\texttt{Mohab.Safey@lip6.fr}
		\end{minipage}
	\end{titlepage}
}

\begin{document}
	\maketitlepage

	\newpage
	\tableofcontents
	\newpage

@@

	\section{MPC-in-the-Head and SBC signature scheme}\label{sec2}
